Verifying Demonstrations

### 2019-02-13 paper/identity-limits.tex
Adds final comment to conclusions in identity-limits
Makes identity-limits conclusions a subsection
Minor clarification to identity-limits

Obviously the one who creates entries in the population registry can do that 
even without such documents, so there must be some separation of duty, 
accountability or transparency to prevent the agency from performing a Sybil 
attack.
In the case of Sweden, the population registry is public.
This means that in addition to any audit trail in place at the agency, we have 
these properties:
\begin{itemize}
  \item The data must fulfil basic integrity: a person must have parents, who 
    in turn must have parents, \etc.
  \item Anyone can detect extraordinary additions, \eg exceptionally many 
    births, additions of family trees, \etc.
    Individual women and men would also notice if extra children were added to 
    them.
  \item Addition of persons of foreign heritage must have corresponding 
    documentation (audit trail) at the Migration Board.
\end{itemize}
A foreign citizen can prove their identity to the Migration Board in the 
following ways:
\begin{itemize}
  \item showing a national passport in the original or
  \item showing an identity document in the original or
  \item a close relative attesting to the 
    identity~\cite{Migrationsverket-ProvenIdentity}.
\end{itemize}
Thus the security is reduced to subverting one of these methods.

@@

\section{Conclusions}

While the decentralized properties of proofs-of-personhood are appealing, it is 
hard to achieve such a scheme.
The goal is to have one identity (pseudonym) per physical person.
This goal is joint with the \enquote{birth-certificate system} which actually 
achieves the goal quite nicely in practice.
However, since the birth-certificate system relies on audit trails to function, 
it cannot deal with issuing anonymous credentials.
Thus the ideas from proof-of-personhood, where everyone must act jointly, can 
solve this problem.
To issue anonymous credentials that certify one physical person behind a 
pseudonym, all issuers must act jointly, \eg through \ac{MPC}.

>>>>

Obviously the one who creates entries in the population registry can do that 
even without such documents, so there must be some separation of duty, 
accountability or transparency to prevent the agency from performing a Sybil 
attack.
In the case of Sweden, the population registry is public.
This means that in addition to any audit trail in place at the agency, we have 
these properties:
\begin{itemize}
  \item The data must fulfil correctness: a person must have parents, who in 
    turn must have parents, \etc.
  \item Anyone can detect extraordinary additions, \eg exceptionally many 
    births, additions of family trees, \etc.
    Individual women and men would also notice if extra children were added to 
    them.
  \item Addition of persons of foreign heritage must have a corresponding audit 
    trail at the Migration Board (separate agency).
\end{itemize}
A foreign citizen can prove their identity to the Migration Board in the 
following ways:
\begin{itemize}
  \item showing a national passport in the original or
  \item showing an identity document in the original or
  \item a close relative attesting to the 
    identity~\cite{Migrationsverket-ProvenIdentity}.
\end{itemize}
Thus the security is reduced to subverting one of these methods.

@@

\subsection{Conclusions}

While the decentralized properties of proofs-of-personhood are appealing, it is 
hard to achieve such a scheme.
The goal is to have one identity (pseudonym) per physical person.
This goal is joint with the \enquote{birth-certificate system} which actually 
achieves the goal quite nicely in practice.
However, since the birth-certificate system relies on audit trails to function, 
it cannot deal with issuing anonymous credentials.
Thus the ideas from proof-of-personhood, where everyone must act jointly, can 
solve this problem.
To issue anonymous credentials that certify one physical person behind a 
pseudonym, all issuers must act jointly, \eg through \ac{MPC}.
We do not see this as something impossible, \eg it can be incorporated into the 
eIDAS regulation already in place in the EU.
